The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
 in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
 can also be realized by oblique jets as the eROSITA bubbles.\

>>>>

 Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
 compared with the observed one\
 in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
 can also be realized by oblique jets as the eROSITA bubbles.\
